\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[a4paper,top=2cm,bottom=2cm,left=2cm,right=2cm,marginparwidth=1.75cm]{geometry}

\usepackage[resetlabels,labeled]{multibib}
\newcites{J}{Journals}
\newcites{I}{International conferences}

% Useful packages
\usepackage{graphicx}
\usepackage{minted}
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
\usepackage[dvipsnames]{xcolor}
\usepackage{xpatch}
\makeatletter
\newcommand\removebibheader
  {\xpatchcmd\std@thebibliography
    {\section*{\refname}%
     \@mkboth{\MakeUppercase\refname}{\MakeUppercase\refname}%
    }{}{}{}%
  }
\makeatother
\hypersetup{
    colorlinks=true,
    linkcolor=JungleGreen,
    filecolor=DarkOrchid,      
    urlcolor=Blue,
    }
\pagenumbering{gobble}
\usepackage[mark]{gitinfo2}

\title{LateX tricks}
\date{}
\begin{document}
\maketitle
\noindent List of references are generated with ChatGPT.\\

\noindent The unsrt bibliography file style was downloaded from: \url{https://mirrors.ctan.org/biblio/bibtex/base/unsrt.bst}.\\

\noindent In this document, I want to:
\begin{enumerate}
    \item Emphasize two imaginary authors: \textbf{John Smith} and \underline{Emily Johnson}.
    \item Separate journals, conferences with different BibTeX keys.
    \item Make references in different subsections.
    \item Add a footer with git information thanks to the \href{https://ctan.org/pkg/gitinfo2}{gitinfo2} package.
\end{enumerate}

\section{How to add other authors?}
Solution from \href{https://www.sethajacobson.com/notes/2021/3/1/to-bold-and-italicize-specific-author-names-in-a-latex-generated-citation}{this blog}. 
\begin{itemize}
    \item Add a macro at the top of the BST file. Name must be \textbf{exactly} like in the bibliography.
    \item Add a line in \texttt{FUNCTION {format.names}} where \texttt{bold.if.jsmith} and \texttt{under.if.ejohnson} are already added.
\end{itemize}
\begin{minted}
[
frame=lines,
framesep=2mm,
baselinestretch=1.2,
]
{latex}
% Add macro to make author underline
FUNCTION {under.if.ejohnson}
    { duplicate$ purify$ 
    "Emily Johnson"
    purify$ = { 
    "\underline{"
    swap$ * "}" * } 'skip$ if$
}
% FUNCTION {format.names}
{ s nameptr "{ff~}{vv~}{ll}{, jj}" format.name$
bold.if.jsmith
under.if.ejohnson
't :=
\end{minted}

\section{How to add other bibliography sections?}
Solution from \href{https://www.overleaf.com/learn/latex/Questions/Creating_multiple_bibliographies_in_the_same_document}{Overleaf}.
\begin{minted}
[
frame=lines,
framesep=2mm,
baselinestretch=1.2,
]
{latex}
\usepackage[resetlabels,labeled]{multibib}
\newcites{Math}{Math Readings}
\newcites{Phys}{Physics Readings}
% [...]
\cite{paper1} and \cite{paper2} were published later than 
\citeMath{paper3}. See also \citePhys{paper4}.
\bibliographystyle{unsrt}
\bibliography{references}
\bibliographystyleMath{unsrt}
\bibliographyMath{refs-etc}
\bibliographystylePhys{unsrt}
\bibliographyPhys{refs-etc}
\end{minted}

\nocite{brown2025ai} \nociteI{brown2031future} \nociteJ{clark2029neural,davis2026robotics,johnson2023deep}
\newpage
\bibliographystyle{myunsrt}
\section{Publications list}
\subsection{Unsorted references}
{\removebibheader
\bibliography{sample}
}
\bibliographystyleI{myunsrt}
\subsection{International conferences}
{\removebibheader
\bibliographyI{sample}
}
\bibliographystyleJ{myunsrt}
\subsection{Journals}
{\removebibheader
\bibliographyJ{sample}
}
\end{document}